Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-02-05 paper/main.tex
WIP discussion updates

The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.  We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and alterations as the explicit content of the video was transformed into participants' memories.  In one analysis we sought to identify brain structures that were sensitive to the dynamic unfolding of the video's content, as characterized by its topic trajectory.  Specifically, we used a searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrix of activity (as participants watched the video) matched the proximal temporal correlation matrix of original video's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).  We then performed a phase shift-based permutation correction to ensure our searchlight procedure identified regions specifically sensitive to the temporal structure of the video (i.e., rather than those with an autocorrelation length similar to the video; see \textit{Methods}).  We $z$-scored the searchlight results at each voxel against the null distribution of (100) permuted searchlight results, thresholding at $p=0.05$. As shown in Figure~\ref{fig:brainz}C, the analysis revealed a distributed network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video.  In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later structure their \textit{recall} of the video.  We used an analogous searchlight procedure and permutation correction to identify clusters of voxels whose proximal temporal correlation matrices reflected the proximal temporal correlation matrix of the topic proportions for each individual's recall (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).  As shown in Figure~\ref{fig:brainz}D, the analysis revealed a network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in transforming each individual's experience into memory.  In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
% ------ NOTE: ------
% Potentially need to fill in ????s with names of structures? But maybe not; better to leave without inference because of neurosynth analysis?
% - Paxton

@@

The set of searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses mirrored to the temporal structure of the video (Fig.~\ref{fig:brainz}C) or participants' eventual recalls (Fig.~\ref{fig:brainz}D).  As an exploratory analysis, we sought to identify structures comprised these networks and what functions are shared among them.  To accomplish this in a blind, unbiased manner (i.e., without reverse inference via visual observation) we used \texttt{Neurosynth} \citep{YarkEtal11}.  \texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms based on NIfTI images accompanying studies where those terms appear at a high frequency.  Given a novel image tagged with its value type (e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} can then \textit{decode} the list of terms whose meta-analysis images are most similar.  We constructed brain maps of voxelwise $p$-values derived from our permutation correction (masking voxels with a corresponding permutation-derived $z$-score at or below zero).  These maps describe the extent to which each voxel specifically reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the percentage of phase-shifted topic vector correlation matrices to which the voxel activity correlation matrix was less similar).  These $p$-value maps for the video- and recall-driven searchlight analyses are displayed in Figure \ref{fig:neurosynth}, along with the top ten terms decoded from each using \texttt{Neurosynth}.

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
\caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} Video-searchlight $p$-map and top 10 decoded terms.  We constructed a map of the permutation-derived $p$-values for the video-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) for all voxels with a positive permutation-derived $z$-score.  The top 10 terms decoded from this $p$-map are shown in red.  \textbf{B.} Recall-searchlight $p$-map and top 10 decoded terms.  We constructed a map of the permutation-derived $p$-values for the recall-driven searchlight analysis (Fig.~\ref{fig:brainz}B, D) for all voxels with a positive permutation-derived $z$-score.  The top 10 terms decoded from this $p$-map are shown in blue.}
\label{fig:neurosynth}
\end{figure}
\FloatBarrier

@@

Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or shape, of an experience.  This view draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.  One approach to identifying neural responses to naturalistic stimuli (including experiences) entails building a model of the stimulus and searching for brain regions whose responses are consistent with the model.  In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have extended this approach with a clever twist: rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.  So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.  By contrast, in our present work we used topic models and HMMs to construct an explicit stimulus model (i.e., the topic trajectory of the video).  When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlapped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in][]{LernEtal11}.  This provides support for the notion that part of the long temporal receptive window network may be maintaining an explicit model of the stimulus dynamics.  When we performed a similar analysis after swapping out the video's topic trajectory with the recall topic trajectories of each individual participant, this allowed us to identify brain regions whose responses (as the participants viewed the video) reflected how the video trajectory would be transformed in memory (as reflected by the recall topic trajectories).  The analysis revealed that the rMTL and vmPFC may play a role in this person-specific transformation from experience into memory.  The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04a, Dava06, WiltSilv07, DianEtal07, KestEtal13}.  Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, KestEtal13, SchlPres15, GilbMarl17, SpalEtal18}.  Integrating across our study and this prior work, one interpretation is that the person-specific transformations mediated (or represented) by the rMTL and vmPFC may reflect schema knowledge being leveraged, formed, or updated, incorporating ongoing experience into previously acquired knowledge.
% Here's a bunch of citations to possibly add to this last sentence, though not sure if we should because the sentence is framed as a "new idea" to come out of this study:
% Takashima et al., 2007 -- vmPFC involved in stabilizing/reorganizing retrieval networks
% Tse et al., 2007; Zeithamova and Preston, 2010; Tse et al., 2011 -- vmPFC involved in integrating featurally similar experiences
% Nieuwenhuis and Takashima, 2011 -- vmPFC activity linked to evaluating memories' relevance to current situation
% Kuhl et al., 2007; Wimber et al., 2008, 2009, 2011, 2015 -- vmPFC and vlPFC inhibit contextually irrelevant memories during retrieval
% -Paxton

In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a high probability of initiating recall with the first video event (Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the event immediately following it (Fig.~\ref{fig:list-learning}B).  However, equally noteworthy are the typical free recall results not recovered in these analyses, as each highlights a fundamental difference between list-learning studies and naturalistic memory paradigms like the one employed in the present study.  The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the video stimulus.  Stimuli in free recall experiments most often comprise lists of simple, common words, presented to participants in a random order. \citep[In fact, numerous word pools have been developed based on these criteria; e.g.,][]{FrieEtal82}.  These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.  First, researchers conducting free recall studies may assume that the content at each presentation index is essentially equal, and does not bear qualities that would cause participants to remember it more or less successfully than others.  Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.  Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of individual stimuli and their presentation positions---in other words, two semantically related words are no more likely to be presented next to each other than at opposite ends of the list.  In most cases, the exact opposite is true of real-world episodes.  Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct, causal progression.  As a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.  Memory literature has termed this strong temporal autocorrelation ``context," and in various media that depict real-world events (e.g., movies and written stories), we recognize it as a \textit{narrative structure}.  While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, starting with the beginning.  This tendency is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).

Thus, analyses such as those in Figure \ref{fig:list-learning} that address only the temporal dynamics of free recall paint an incomplete picture of memory for naturalistic episodes.  While useful for studying presentation order-dependent recall dynamics, they neglect to consider the stimuli's content (or, for example, that content's potential interrelatedness).  However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (i.e., an event) that is considered to have been ``remembered."  When modeling memory experiments, often times events (or items) and their later memories are treated as binary and independent events (e.g., a given list item was simply either remembered or not remembered).  Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering this binary judgement instead categorical.  Our novel framework allows one to assess memory performance in a more continuous way (\textit{precision}), as well as analyze the correlational structure of each encoding event to each memory event (\textit{distinctiveness}). Further and importantly, these two novel metrics we introduce here arise from comparisons of the actual content of the experience/memories, which is not typically modeled.  Leveraging this, we find that the successful memory performance is related to 1) the precision with which the participant recounts each event and 2) the distinctiveness of each recall event (relative to the other recalled events). The first finding suggests that the information retained for \textit{any individual event} may predict the overall amount of information retained by the participant.  The second finding suggests that the ability to distinguish between temporally or semantically similar content is also related to the quantity of content recovered. Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.  Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.
% ------ NOTE: ------
% need to update text here to reflect new distinctivness stats in precision/distinctiveness fig
% - Paxton

% NOTE: do you know of a good reference for WAS and word2vec ?
% SteyEtal04 = WAS; MikoEtal13 = word2vec
% -Paxton
While a large number of language models exist \citep[e.g., WAS, LSA, word2vec, universal sentence encoder;][]{SteyEtal04, LandEtal98, MikoEtal13, CerEtal18}, here we use latent dirichlet allocation (LDA)-based topic models for a few reasons.  First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.  This was an important feature of our model since different people may accurately recall a scene using very different language. Second, words can mean different things in different contexts (e.g. ``bat" as the act of hitting a baseball, the object used for that action, or as a flying mammal).  Topic models are robust to this, allowing words to exist as part of multiple topics.  Last, topic models provide a straightforward means to recover the weights for the particular words comprising a topic, enabling easy interpretation of an event's contents (e.g. Fig.~\ref{fig:topics}). Other models such as Google's universal sentence encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward. However, it's worth pointing out that our framework is divorced from the particular choice of language model. Moreover, many of the aspects of our framework could be swapped out for other choices. For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized for the particular problem. Indeed for some problems, recovery of the particular recall words may not be necessary, and thus other text-modeling approaches (such as universal sentence encoder) may be preferable. Future work will explore the influence of particular model choices on the framework's accuracy.

>>>>

The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories.  We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and transformations between the external world and memory.  In one analysis, we sought to identify brain structures that were sensitive to the dynamic unfolding of the video's content, as characterized by its topic trajectory.  We used a searchlight procedure to identify clusters of voxels whose activity patterns displayed a proximal temporal correlation structure (as participants watched the video) matching that of the original video's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).  In a second analysis, we sought to identify brain structures whose responses (during video viewing) reflected how each participant would later structure their \textit{recalls} of the video.  We used an analogous searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions for each individual's recall (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).  To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the video or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the video/recalls), we performed a phase shift-based permutation correction (see \textit{Methods} for additional details).  Specifically, we circularly shifted the timeseries of the topic trajectory by a random number of timepoints, recomputed the shifted trajectory's correlation matrix, and again performed our searchlight analysis on this permuted data.  We then $z$-scored the ``real" searchlight results at each voxel against the null distribution of (100) permuted results.  In Figure~\ref{fig:brainz}, only voxels whose activity pattern reflected the ``real" video/recall timeseries more closely than 95\% of the permuted results are shown.  As shown in Figure~\ref{fig:brainz}C, the video-driven searchlight analysis revealed a distributed network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video. As shown in Figure~\ref{fig:brainz}D, the analysis revealed a network of regions including \textbf{\textit{????}}, suggesting that these regions facilitate a person-specific transformation of one's experience into memory.  In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
% ------ NOTE: ------
% Potentially need to fill in ????s with names of structures? But maybe not; better to leave without inference because of neurosynth analysis?
% - Paxton

@@

The searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses mirrored to the temporal structure of the video (Fig.~\ref{fig:brainz}C) or participants' eventual recalls (Fig.~\ref{fig:brainz}D).  We next sought to gain greater insight into the structures and functional networks our results reflected.  To accomplish this in a blind, unbiased manner (i.e., without reverse inference via visual observation) we performed an additional, exploratory analysis using \texttt{Neurosynth} \citep{YarkEtal11}.  \texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.  Then, given a novel image (tagged with its value type; e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar to this new data.  Our permutation procedure (described above) yielded, for each of the two searchlight analyses, a voxelwise map of significance ($p$-statistic) values.  These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the proportion of phase-shifted topic vector correlation matrices less similar to the voxel activity correlation matrix than the unshifted video's correlation matrix).  These significance maps for the video- and recall-driven searchlight analyses, along with the 10 terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:neurosynth}.

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
\caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} Video-searchlight significance and top 10 decoded terms.  We constructed a map of the permutation-derived $p$-values for the video-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) at each voxel with a positive permutation-derived $z$-score.  The top 10 terms decoded from this significance map are shown in red.  \textbf{B.} Recall-searchlight significance and top 10 decoded terms.  We constructed a map of the permutation-derived $p$-values for the recall-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) at each voxel with a positive permutation-derived $z$-score.  The top 10 terms decoded from this significance map are shown in blue.}
\label{fig:neurosynth}
\end{figure}
\FloatBarrier

@@

Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or shape, of an experience.  This view draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.  One approach to identifying neural responses to naturalistic stimuli (including experiences) entails building a model of the stimulus and searching for brain regions whose responses are consistent with the model.  In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have extended this approach with a clever twist: rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.  So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.  By contrast, in our present work we used topic models to construct an explicit content model directly from the stimulus (i.e., the topic trajectory of the video).  Projecting each participant's recall into a space shared by both the stimulus and other participants then allows us to compare recalls both directly to the stimulus and to each other.  Similarly, prior work introducing the use of HMMs to discover latent event structure in naturalistic stimuli and recall \citep{BaldEtal17} used a between-subjects cross-validation approach to identify event boundaries shared across participants, and between stimulus and recall.  Our framework allows us to break from the restriction of a common, shared event-timeseries and identify the unique \textit{resolution} of each participant's recall event structure, and how that may differ from the video and each other.  
% @JEREMY @ANDY PLEASE CHECK THIS TO MAKE SURE I'M NOT MISCHARACTERIZING BALDETAL17

In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a heightened probability of initiating recall with the first presented ``item" (in our case, video events; Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the one immediately following it (Fig.~\ref{fig:list-learning}B).  However, equally noteworthy are the typical free recall results \textit{not} recovered in these analyses, as each highlights a fundamental difference between the list-learning paradigm and naturalistic memory paradigms like the one employed in the present study.  The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the video.  Stimuli in free recall experiments most often comprise lists of simple, common words, presented to participants in a random order. \citep[In fact, numerous word pools have been developed based on these criteria; e.g.,][]{FrieEtal82}.  These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.  First, researchers conducting free recall studies may assume that the content at each presentation index is essentially equal, and does not possess attributes that would render it, on average, more or less memorable than others.  Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.  Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of individual stimuli and their presentation positions---in other words, two successively presented items are no more likely to be highly semantically similar than they are to be high dissimilar.  In most cases, the exact opposite is true of real-world episodes.  Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct, causal progression.  As a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.  Memory literature has termed this strong temporal autocorrelation ``context," and in various media that depict real-world events (e.g., movies or written stories), we recognize it as a \textit{narrative structure}.  While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, starting with the beginning.  This tendency is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).

Because they disregard presentation order-dependent variability in the stimulus content, analyses such as those in Figure \ref{fig:list-learning} enable a more sensitive analysis of presentation order-dependent temporal dynamics in free recall. Yet by the same token, they paint a wholly incomplete picture of memory for naturalistic episodes.  In an attempt to address this shortcoming, we have developed a framework in the present study that characterizes the explicit semantic content of the stimulus and subsequent recalls.  However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (e.g., an event) that is considered to have been ``remembered."  When modeling memory in an experimental setting, recall quality for individual events is often cast as binary (e.g., a given list item was simply either remembered or not remembered).  Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering this binary judgement instead categorical.  To better evaluate naturalistic memory quality, we introduce a continuous metric (\textit{precision}), which reflects the level of completeness of a participant's recall for a feature-rich experience.  Additionally, recall quality for a single event is typically assessed independently from that for all other events (e.g., it is difficult to ``compare" a participant's binary recall success for list item 1 to that of list item 10).  The second novel metric we introduce (\textit{distinctiveness}) is based on analyzing of the correlational structure of an individual's full set of recall events, and reflects the specificity of their memory for a single experienced event.  We find that the successful memory performance is related to 1) the precision with which the participant recounts each event and 2) the distinctiveness of each recall event (relative to the other recalled events). The first finding suggests that the information retained for \textit{any individual event} may predict the overall amount of information retained by the participant.  The second finding suggests that the ability to distinguish between temporally or semantically similar content is also related to the quantity of content recovered. Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.  Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.

While a large number of language models exist \citep[e.g., WAS, LSA, word2vec, universal sentence encoder;][]{SteyEtal04, LandEtal98, MikoEtal13, CerEtal18}, here we use latent dirichlet allocation (LDA)-based topic models for a few reasons.  First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.  This was an important feature of our model since different people may accurately recall a scene using very different language. Second, words can mean different things in different contexts (e.g. ``bat" may be the act of hitting a baseball, the object used for that action, or as a flying mammal).  Topic models are robust to this, allowing words to exist as part of multiple topics.  Last, topic models provide a straightforward means to recover the weights for the particular words comprising a topic, enabling easy interpretation of an event's contents (e.g. Fig.~\ref{fig:topics}). Other models such as Google's Universal Sentence Encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward. However, it's worth pointing out that our framework is divorced from the particular choice of language model. Moreover, many of the aspects of our framework could be swapped out for other choices. For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized for the particular problem. Indeed for some problems, recovery of the particular recall words may not be necessary, and thus other text-modeling approaches (such as universal sentence encoder) may be preferable. Future work will explore the influence of particular model choices on the framework's efficacy.

When we searched for brain structures whose responses are consistent with the video and recall topic trajectories, we identified two diffuse networks of regions \textbf{\textit{INSERT SOME BETTER COMMENTARY HERE}} (Fig.~\ref{fig:brainz}C,D).  Decoding the significance maps (Fig.~\ref{fig:neurosynth}) revealed two interesting results.  The significant

% Here's a bunch of citations to possibly add to this last sentence, though not sure if we should because the sentence is framed as a "new idea" to come out of this study:
% Takashima et al., 2007 -- vmPFC involved in stabilizing/reorganizing retrieval networks
% Tse et al., 2007; Zeithamova and Preston, 2010; Tse et al., 2011 -- vmPFC involved in integrating featurally similar experiences
% Nieuwenhuis and Takashima, 2011 -- vmPFC activity linked to evaluating memories' relevance to current situation
% Kuhl et al., 2007; Wimber et al., 2008, 2009, 2011, 2015 -- vmPFC and vlPFC inhibit contextually irrelevant memories during retrieval
% -Paxton
